\section*{Abstract}
The goal of this study is to design and implement an end-to-end facial recognition system.
The first part is focused on a general overview of modern methods followed by an in-depth description of
state-of-the-art research of loss functions.
The emphasis is being put on the ArcFace loss as it is the research which forms the basis of the facial recognition
system implemented in this thesis.
The second part deals with the design and implementation of the system.
The end of the text contains a comparison with a commercial algorithm.
The performance was evaluated on a dataset which was created from the recordings of evening news on the czech public
television broadcast (Česká Televize).

\vspace{1cm}

\subsection*{Key words}
Machine learning, facial recognition, identification, verification, convolutional neural networks, loss functions,
ArcFace

\vfill

\section*{Abstrakt}
Cílem této práce je návrh a implementace systému rozpoznávání obličeje.
V první části je poskytnut přehled moderních metod, na který navazuje podrobný rozbor výzkumu ztrátových funkcí.
Důraz je kladen na ztrátovou funkci ArcFace.
Tato funkce byla použita při trénování modelu, jenž tvoří jádro systému implementovaného v rámci této práce.
Druhá část práce obsahuje návrh a popis implementace systému.
V závěru je systém porovnán s komerčním algoritmem.
Vyhodnocení proběhlo na datasetu, jenž byl vytvořen ze záznamu večerních zpráv České Televize.

\vspace{1cm}

\subsection*{Klíčová slova}
Strojové učení, rozpoznávání obličeje, identifikace, verifikace, konvoluční neuronové sítě, ztrátové funkce, ArcFace