\chapter{Introduction}\label{ch:introduction}
\pagenumbering{arabic}
Facial recognition systems recently exceeded the performance of humans on many real-world benchmarks.

The beginning of the quest to give computers the ability to recognize human faces dates back to the 1960s~\cite{History}
with Woody Bladson being the first researcher to attempt the feat.
The issue with the first systems was the decrease of performance when the faces were not in the optimal position.
A big stepping stone towards pose invariance came with the invention of convolutional neural networks~\ref{ch:cnn}.
These models are the cornerstone of modern computer vision.

In the field of facial recognition, a lot of effort was put into the design of loss functions.
These functions are essential in all of the machine learning, for they are used to supervise model fitting.
The researcher's goal is to design this function in such a way that mathematical optimization leads to the model
with desired properties.
In the last few years, as is manifested in the superhuman performance of these models, the research was very successful.
An impressive property of these systems is the grace with which they generalize beyond faces present in the training
dataset.
This makes it much easier to determine that the person is not in the set of known identities.
This is crucial for biometric authentication.

The improved accuracy and reliability of facial recognition technology led to a widespread deployment of these systems.
These systems found their place in our phones giving them the ability to unlock automatically;
they found a place on the servers of big technology companies, like Google who uses the technology to better organize
our photos;
the technology is also at the heart of modern surveillance systems.

The last-mentioned use case is the reason why the deployment of these algorithms is plagued by controversy.
As the saying goes, technology is a double edged sword.
Facial recognition is the embodiment of this saying.
On the positive side, there were many cases in which the technology helped authorities capture dangerous
individuals~\cite{FacRecCon}.
However, no matter how good this benefit is, for many, it is not worth the risk of losing the privacy.
This is the case in San Francisco, where the legislators voted to ban the use of the technology by
law enforcement~\cite{FacRecSan}.


\section{Goals}\label{sec:goals}
The goals of this thesis are:
\begin{enumerate}
    \item to provide an overview of modern facial recognition methods;
    \item to implement a state-of-the-art algorithm;
    \item to evaluate the system's performance on appropriate benchmark dataset;
    \item to compare the results with commercial algorithm.
\end{enumerate}

\section{Outline}\label{sec:outline}
This text consists of seven chapters with introduction being the first one.

The second chapter is about convolutional neural networks and the different types of layers hidden within their
architecture.

In the third chapter I provide an overview of the chain of processes constituting typical facial recognition system
(pipeline).
In this chapter there is also a description of the most important benchmarking datasets and selected commercial
systems.

Fourth chapter is a description of losses used in facial recognition tasks and the ideas leading to them.
At the end of the chapter, there is a description of ArcFace research.
This research plays an essential part in this project because the model used at the core of the system I have
implemented was trained under the supervision of ArcFace loss.

In the fifth chapter, I define metrics which are later used for system evaluation.

The sixth chapter contains a description of the algorithm I have implemented.
At the end of the chapter, there is a comparison with the commercial algorithm.

The last chapter is a conclusion.